A 30 Million Year Old Mini-Neptune in the Kepler Field

### 2021-05-21 paper/ms.tex
gptransit v2
* updated LD
* rho prior fixed to avoid the nonperiodic SHOTerm competing with the
periodic one

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded transit of Kepler 1627b, with stellar
    variability removed.}  
    The 1-$\sigma$ model uncertainties (faint purple band) and the
    median model are shown.
		\label{fig:phasefold}
	}
\end{figure*}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded transit of Kepler 1627b, with stellar
    variability removed.}  
    The 1-$\sigma$ model uncertainties and the median model are shown
    as the faint purple band, and the dark purple line.
    Gray points are individual \texttt{PDCSAP} flux measurements;
    black points are binned to 20 minutes, with a representative error
    bar shown.
		\label{fig:phasefold}
	}
\end{figure*}

We assumed a quadratic limb-darkening law, with the uninformative prior
advocated by CITET Kipping2013.

% In the first approach, we adopted uniform priors centered on the
% interpolated CITET Claret+2011 coefficients in the Kepler-band, with
% with $\pm 0.2$ in either parameter.  The fit was not as good.
